\problemname{Mutex}
Anna loves coding multithreaded backend services.
In such a service, multiple threads may sometime need to read and write the same data structures in memory.
To ensure all threads have a consistent view of a single datastructure, one can use so-called \emph{mutexes} to protect access to it.

A mutex is an object that threads can \emph{acquire} and \emph{release}.
When a mutex is acquired, the mutex cannot be acquired again until it is released -- even by the same thread!
If a thread attempts to acquire a mutex it has already acquired, the thread will \emph{deadlock}, waiting for itself to release the mutex.

Anna has written a program that consists of a number of functions.
Each function consists of a list of commands that execute sequentially when the function is called.
The commands are each one of:
\begin{itemize}
  \item acquire the mutex named $X$
  \item release the mutex named $X$
  \item access a data structure protected by the mutex $X$
  \item call another function
\end{itemize}

Anna is unsure regarding whether she implemented her mutexes correctly.
She wants your help to verify that three properties hold.
Assuming a function \texttt{main} is called in the beginning of the program, you should check whether;
\begin{enumerate}
  \item whenever a data structure protected by a mutex $X$ is to be accessed, the mutex $X$ is currently acquired,
  \item whenever a mutex is to be acquired, the program has not already acquired it, causing a deadlock,
  \item whenever a mutex is to be released, the program is currently holding it.
\end{enumerate}

\section*{Input}
The first line of the input contains an integer $N$, the number of functions.
This is followed by a description of all the $N$ functions.

The description of a function starts with an integer $M$ and a string $X$, meaning that there is a function named $X$ with $M$ commands.
This is followed by $M$ lines, each containing a command.
The commands will be of the form:
\begin{itemize}
  \item \texttt{acquire X} -- the mutex named $X$ is acquired
  \item \texttt{release X} -- the mutex named $X$ is released
  \item \texttt{access X} -- a data structure that must be protected by the mutex $X$ is accesses
  \item \texttt{call F} -- the function called $F$ is called
\end{itemize}

All functions and mutexes have names between $1-10$ in length containing only characters \texttt{a-z}.
No two functions will have the same name, and there will always be a function called \texttt{main}.

It is guaranteed that there is no infinite recursion: a function will never call itself, either directly or through a chain of other functions.

\section*{Output}
If all properties hold, output \texttt{a-ok}.

Otherwise, for each property that does not hold, if
\begin{enumerate}
  \item a data structure may be accessed without the correct mutex being acquired, output \texttt{corruption},
  \item a deadlock may occur, output \texttt{deadlock},
  \item a mutex may be released without being acquired, output \texttt{error}.
\end{enumerate}

If several properties does not hold, you should output the above messages on separate lines, in that order.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points.
To get the points for a test group you need to solve all test cases in the test group.
Your final score will be the maximum score of a single submission.

\noindent
\begin{tabular}{| l | l | l | l |}
\hline
Group & Points & Constraints \\ \hline
% Simulera händelseförloppet
1     & ??     & The number of instructions among all functions are at most 10. \\ \hline
% Enkel begränsning, gör att man kan göra DP över vart man är och om den enda mutexen hålls.
2     & ??     & There is only a single mutex, and the number of instructions among all functions are at most $50\,000$. \\ \hline
% Naiv Kubiskt
3     & ??     & The number of instructions among all functions are at most 500. \\ \hline
% Naiv kvadratisk
4     & ??     & The number of instructions among all functions are at most $10\,000$. \\ \hline
% Konstaktfaktoroptimeringar? Bitsets?
5     & ??     & The number of instructions among all functions are at most $50\,000$. \\ \hline
\end{tabular}
